NaiveBayes

### 2020-09-20 DATA622/M03-nb-script.rmd
Modified file path

# usage isOverfitting(tr.cfm,tst.cfm)
```{r}
isOverfitting<-function(trcfm,tstcfm)
{
  # if the accuracy from training is much more than accuracy testing phase
  # then we conclude Model is overfitting 
  # unable to generalize
  tracc=trcfm$overall['Accuracy']
  tstacc=tstcfm$overall['Accuracy']
  tracc > 2*tstacc 
}
```
# usage isUnderfitting(tr.cfm)
```{r}
isUnderfitting<-function(trcfm)
{
  # if the accuracy from training is much more than accuracy testing phase
  # then we conclude Model is overfitting 
  # unable to generalize
  tracc=trcfm$overall['Accuracy']
  0.5 >  tracc
}
```
# Load data and EDA
Let us load the data.
And subset it to include only categorical predictors.
```{r}
file<-'c:/Users/rkannan/rk/data/heart.csv'
heart<-read.csv(file,head=T,sep=',',stringsAsFactors=F)
head(heart)
catheart<-heart[,c(2,3,6,7,9,11,12,13,14)]
```
#Preliminary EDA

>>>>

# usage isOverfitting(tr.cfm,tst.cfm)
```{r}
isOverfitting<-function(trcfm,tstcfm)
{
  # if the accuracy from training is much more than accuracy testing phase
  # then we conclude Model is overfitting 
  # unable to generalize
  tracc=trcfm$overall['Accuracy']
  tstacc=tstcfm$overall['Accuracy']
  tracc > 2*tstacc 
}
```
# usage isUnderfitting(tr.cfm)
```{r}
isUnderfitting<-function(trcfm)
{
  # if the accuracy from training is much more than accuracy testing phase
  # then we conclude Model is overfitting 
  # unable to generalize
  tracc=trcfm$overall['Accuracy']
  0.5 >  tracc
}
```
# Load data and EDA
Let us load the data.
And subset it to include only categorical predictors.
```{r}
file<-'heart.csv'
heart<-read.csv(file,head=T,sep=',',stringsAsFactors=F)
head(heart)
catheart<-heart[,c(2,3,6,7,9,11,12,13,14)]
```
#Preliminary EDA
